Exact Phylodynamic Likelihood\\ via Structured Markov Genealogy Processes

### 2024-06-12 ms.Rnw
phylopomp 0.14.2.3

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.4")
stopifnot(packageVersion("pomp")>="5.9")
stopifnot(packageVersion("phylopomp")>="0.13.2")
theme_set(theme_bw(base_family="serif"))
options(
  width=150,
  keep.source=TRUE,
  encoding="UTF-8",
  stringsAsFactors=FALSE,
  dplyr.summarise.inform=FALSE,
  pomp_archive_dir="results"
)
set.seed(1159254136)
@

@@

\begin{figure}
  \begin{center}
    <<geneal,fig.dim=c(4,2),out.width="50%">>=
    freeze(
      seed=382490723,
      simulate(
        "SEIR",
        Beta=3,sigma=0.5,gamma=0.2,psi=0.3,omega=0.5,
        S0=15,E0=1,I0=2,R0=0,
        time=10
      )
    ) -> x

@@

\begin{figure}
  <<upo,fig.dim=c(4,6),out.width="50%">>=
  freeze(
    seed=522390503,
    simulate(
      "SEIR",
      Beta=1,sigma=0.5,gamma=0.1,psi=0.4,omega=0.1,
      S0=10,E0=1,I0=1,R0=0,
      time=10
    )
  ) -> x

>>>>

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.4")
stopifnot(packageVersion("pomp")>="5.9.1")
stopifnot(packageVersion("phylopomp")>="0.14.2.3")
theme_set(theme_bw(base_family="serif"))
options(
  width=150,
  keep.source=TRUE,
  encoding="UTF-8",
  stringsAsFactors=FALSE,
  dplyr.summarise.inform=FALSE,
  pomp_archive_dir="results"
)
set.seed(1159254136)
@

@@

\begin{figure}
  \begin{center}
    <<geneal,fig.dim=c(4,2),out.width="50%">>=
    simulate(
      "SEIR",
      Beta=3,sigma=0.5,gamma=0.2,psi=0.3,omega=0.5,
      S0=15,E0=1,I0=2,R0=0,
      time=10
    ) |>
      freeze(seed=382490723) -> x

@@

\begin{figure}
  <<upo,fig.dim=c(4,6),out.width="50%">>=
  simulate(
    "SEIR",
    Beta=1,sigma=0.5,gamma=0.1,psi=0.4,omega=0.1,
    S0=10,E0=1,I0=1,R0=0,
    time=10
  ) |>
    freeze(seed=522390503) -> x
